---
title: "assignment 1"
author: "wang yuhang"
date: "2024-10-04"
output:
  html_document:
    toc: true
    number_sections: true
    df_print: paged
  pdf_document:
    toc: true
  word_document:
    toc: true
    number_sections: true
---
# Assignment 01

The **diamonds** case study
This case study is dataframe with rows and variables (sample space within brackets):

  - price: price in US dollars ($326–$18,823)
  
  - arat: weight of the diamond (0.2–5.01)
  
  - cut: quality of the cut (Fair, Good, Very Good, Premium, Ideal)
  
  - color: diamond colour, from D (best) to J (worst)
  
  - clarity: a measurement of how clear the diamond is (I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best))
  
  - x: length in mm (0–10.74)
  
  - y: width in mm (0–58.9)
  
  - z: depth in mm (0–31.8)
  
  - depth: total depth percentage = z / mean(x, y) = 2 * z / (x + y) thus (43–79)
  
  - table: width of top of diamond relative to widest point (43–95)
  
After downloading from myAriel the diamondsDF.RData file into the working directory, load this dataset into the workspace.


## Get dataset
```{r}
# which is the working directory?
getwd()
dir()

load(file = "data/diamondsDF.RData")

dim(diamondsDF)

names(diamondsDF)

head(diamondsDF)

tail(diamondsDF)

str(diamondsDF)
```
## Univariate frequency distributions

For distinct values of a variable , consider:

- Absolute frequency of value

- Relative frequency

- Cumulative absolute frequency

- Cumulative relative frequency

- Mode

Calculate the above statistics for the following variables:

- **cut**

- **color**

- **clarity**

```{r}
cat("Absolute frequency of cut\n")
ferqCut <- xtabs(~ cut,
                data = diamondsDF)

ferqCut


cat("Absolute frequency of color\n")
ferqColor <- xtabs(~ color,
                data = diamondsDF)

ferqColor

cat("Absolute frequency of clarity\n")

ferqClarity <- xtabs(~ clarity,
                data = diamondsDF)

ferqClarity

```
```{r}
#Relative frequency
cat("Relative frequency of cut\n")
round(100*(ferqCut/ sum(ferqCut)),3)

#Relative frequency
cat("Relative frequency of color\n")
round(100*(ferqColor/ sum(ferqColor)),3)

#Relative frequency
cat("Relative frequency of clarity\n")
round(100*(ferqClarity/ sum(ferqClarity)),3)
```

```{r}
#Cumulative absolute frequency
cat("Cumulative absolute frequency of cut\n")
ferqACut <- cumsum(ferqCut)
ferqACut

#Cumulative absolute frequency
cat("Cumulative absolute frequency of color\n")
ferqAColor <- cumsum(ferqColor)
ferqAColor

#Cumulative absolute frequency
cat("Cumulative absolute frequency of clarity\n")
ferqAClarity <- cumsum(ferqClarity)
ferqAClarity

```
```{r}
#Cumulative relative frequency
cat("Cumulative relative frequency of cut\n")
ferqRelCut <- cumsum(ferqCut)/sum(ferqCut)
ferqRelCut


#Cumulative relative frequency
cat("Cumulative relative frequency of color\n")
ferqRelColor <- cumsum(ferqColor)/sum(ferqColor)
ferqRelColor


#Cumulative relative frequency
cat("Cumulative relative frequency of clarity\n")
ferqRelClarity <- cumsum(ferqClarity)/sum(ferqClarity)
ferqRelClarity


```

```{r}
cat("mode-Cut\n")
freqRel <- ferqCut/ sum(ferqCut)
res <- which(freqRel == max(freqRel))

c(max_frequency = max(freqRel),
  modal_value =names(res),
  position = as.numeric(res))

cat("mode-Color\n")
freqRel <- ferqColor/ sum(ferqColor)
res2 <- which(freqRel == max(freqRel))

c(max_frequency = max(freqRel),
  modal_value =names(res2),
  position = as.numeric(res2))

cat("mode-Clarity\n")
freqRel <- ferqClarity/ sum(ferqClarity)
res3 <- which(freqRel == max(freqRel))

c(max_frequency = max(freqRel),
  modal_value =names(res3),
  position = as.numeric(res3))
```
## Quantitative variables
Now consider these summaries:

- Mean

- Median 

- Maximum 

- Minimum 

- Range = with (distinct values)

- Inter-Quartile Range

- Quantile

- Variance

- Standard deviation
- Coefficient of variation 

Calculate the above statistics for the following variables:

- **price**
- **carat**


```{r}
cat("price mean\n")
mean(diamondsDF$price, na.rm = TRUE)
cat("price median\n")
median(diamondsDF$price, na.rm = TRUE)
cat("price var\n")
var(diamondsDF$price, na.rm = TRUE)
cat("price sd\n")
sd(diamondsDF$price, na.rm = TRUE)
cat("price range\n")
range(diamondsDF$price, na.rm = TRUE)

cat("carat mean\n")
mean(diamondsDF$carat, na.rm = TRUE)
cat("carat median\n")
median(diamondsDF$carat, na.rm = TRUE)
cat("carat var\n")
var(diamondsDF$carat, na.rm = TRUE)
cat("carat sd\n")
sd(diamondsDF$carat, na.rm = TRUE)
cat("carat range\n")
range(diamondsDF$carat, na.rm = TRUE)

```
```{r}
#Q3-Q1
cat("price IQR\n")
IQR(diamondsDF$price, na.rm = TRUE)

quantile(diamondsDF$price, prob=0.25, na.rm = TRUE)
quantile(diamondsDF$price, prob=0.75, na.rm = TRUE)

#Q3-Q1
cat("carat IQR\n")
IQR(diamondsDF$carat, na.rm = TRUE)

quantile(diamondsDF$carat, prob=0.25, na.rm = TRUE)
quantile(diamondsDF$carat, prob=0.75, na.rm = TRUE)
```
```{r}
#Coefficient of Variation--the bigger the less stable
cat("price Coefficient of Variation\n")
100*sd(diamondsDF$price, na.rm = TRUE)/ mean(diamondsDF$price, na.rm = TRUE)

#Coefficient of Variation--the bigger the less stable
cat("carat Coefficient of Variation\n")
100*sd(diamondsDF$carat, na.rm = TRUE)/ mean(diamondsDF$carat, na.rm = TRUE)
```
```{r}
cat("price summary\n")
summary(diamondsDF$price)
cat("carat summary\n")
summary(diamondsDF$carat)
```
