---
title: "assignment 2"
author: "wang yuhang"
date: "2024-10-04"
output:
  word_document:
    toc: true
    number_sections: true
  pdf_document:
    toc: true
  html_document:
    toc: true
    number_sections: true
    df_print: paged
---

# Assignment 02

The diamonds case study
This case study is dataframe with rows and variables (sample space within brackets):

  - price: price in US dollars ($326–$18,823)
  
  - arat: weight of the diamond (0.2–5.01)
  
  - cut: quality of the cut (Fair, Good, Very Good, Premium, Ideal)
  
  - color: diamond colour, from D (best) to J (worst)
  
  - clarity: a measurement of how clear the diamond is (I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best))
  
  - x: length in mm (0–10.74)
  
  - y: width in mm (0–58.9)
  
  - z: depth in mm (0–31.8)
  
  - depth: total depth percentage = z / mean(x, y) = 2 * z / (x + y) thus (43–79)
  
  - table: width of top of diamond relative to widest point (43–95)
  
After downloading from myAriel the diamondsDF.RData file into the working directory, load this dataset into the workspace.

## E00

Calculate the joint frequency distribution for the three variables cut, color and clarity
Transform such R object into a flat table
```{r}
getwd()
dir()
load("data/diamondsDF.RData")
diamondsDF_new <- diamondsDF
head(diamondsDF_new)
```
```{r}
#joint frequency distribution
count_mat <- as.matrix(
ftable(xtabs(~ cut+color+clarity,
      data = diamondsDF_new)))
count_mat
```

## E01

Calculate the percentage for values of clarity conditional on cut=Good and color=D
```{r}
specific_num <- count_mat["Good_D", ]
sum_num <- count_mat[ , ]

cat("the percentage for values of clarity conditional on cut=Good and color=D\n")
round(100*sum(specific_num)/sum(sum_num),3)
```

## E02

Build a barplot for such percentage values with a box around it, and where bars are filled by 12 lines per inch with slope of lines 45 degrees; the main title is “Distribution of clarity given cut=Good and color=D”
```{r}

specific_num <- count_mat["Good_D", ]
specific_num

barplot(specific_num,
        ylim = c(0,250),
        xlim = c(0,10),
        col = grDevices::palette.colors(9,"Polychrome 36"),
        ylab = "Numaber of Good_D",
        xlab = "types of clarity",
        legend.text = "Good_D",
        args.legend = list(x="right"),
        angle = 45,
        density = 12,
        main = "Distribution of clarity given cut=Good and color=D "
)
box()
```

## E03

Find the mode of this distribution
```{r}
#mode
freqRel <- specific_num/ sum(specific_num)
res_new <- which(freqRel == max(freqRel))

c(max_frequency = max(freqRel),
  modal_value =names(res_new),
  position = as.numeric(res_new))
```

## E04

Calculate the cumulative distribution of relative frequencies for the above distribution of clarity, rounded to 4 digits
```{r}

ferqRelclarity <- cumsum(specific_num)/sum(specific_num)
round(ferqRelclarity,4)

```


## E05

Build a histogram of relative frequencies for the variable price, using 6 elements in the partition of the sample space (same size); main title “Histogram of price”; label below the horizontal axis “Price”; fill bars with orange
```{r}
data_price <- diamondsDF_new$price
breaks_custom <- seq(min(data_price), max(data_price), length.out = 7)
hist(data_price, 
     breaks = breaks_custom,
     main = "Histogram of price",  
     xlab = "Price",             
     ylab = "Frequency",          
     col = "orange")                  
```


## E06

Build a scattergram of price (vertical axis) and carat (horizontal axis); the size of plotted characters should be 1/10 of the standard size; points associated with different values of carat should have a different color
```{r}
data_price <- diamondsDF_new$price
data_carat <- diamondsDF_new$carat
# create a color gradient
color_palette <- colorRampPalette(c("purple","lightblue","green","yellow", "red"))

# accordance with the values of carat to set the number of color
n_colors <- length(unique(diamondsDF_new$carat))
plot(data_carat,
     data_price,
     main = "scattergram of price (vertical axis) and carat (horizontal axis)",
     col = color_palette(n_colors)[as.numeric(cut(diamondsDF_new$carat, n_colors))],
     cex = 0.1)

```

## E07

Build a conditional plot of price (vertical axis) and carat (horizontal axis) given cut
```{r}
data_price <- diamondsDF_new$price
data_carat <- diamondsDF_new$carat
data_cut <- diamondsDF_new$cut
levels(data_cut)
cut_fair <- subset(diamondsDF, cut == "Fair")
cut_good <- subset(diamondsDF, cut == "Good")
cut_very_good <- subset(diamondsDF, cut == "Very Good")
cut_premium <- subset(diamondsDF, cut == "Premium")
cut_ideal <- subset(diamondsDF, cut == "Ideal")

plot(cut_fair$carat, cut_fair$price,
     main = "Price vs. Carat by Cut", 
     xlab = "Carat", 
     ylab = "Price",
     col = "#119DA4", 
     pch = 22,
     cex = 1,
     xlim = range(diamondsDF$carat), 
     ylim = range(diamondsDF$price))

points(cut_good$carat, cut_good$price, col = "#FF6F61", pch = 23, cex = 0.6)
points(cut_very_good$carat, cut_very_good$price, col = "#6B5B95", pch = 24, cex = 0.6)
points(cut_premium$carat, cut_premium$price, col = "#88B04B", pch = 25, cex = 0.4)
points(cut_ideal$carat, cut_ideal$price, col = "#E9C46A", pch = 21, cex = 0.2)
#A few more harmonious colors
legend("topright", legend = c("Fair", "Good", "Very Good", "Premium", "Ideal"),
       col = c("#119DA4", "#FF6F61", "#6B5B95", "#88B04B", "#E9C46A"), 
       pch = c(22, 23, 24, 25, 21))
```

## E08

Save the plot at point (8) into a png file where width and height are 2480 pixels after choosing a convenient pointsize
```{r}
png(file="images/scatterPlot.png",
    width = 2480,
    height = 2480,
    units = "px",
    pointsize = 80)
data_price <- diamondsDF_new$price
data_carat <- diamondsDF_new$carat
# create a color gradient
color_palette <- colorRampPalette(c("purple","lightblue","green","yellow", "red"))

# accordance with the values of carat to set the number of color
n_colors <- length(unique(diamondsDF_new$carat))
plot(data_carat,
     data_price,
     main = "Scattergram of price and carat",
     col = color_palette(n_colors)[as.numeric(cut(diamondsDF_new$carat, n_colors))],
     cex = 0.1)
box()
dev.off()
```

```{r}
png(file="images/ConditionalPlot.png",
    width = 2480,
    height = 2480,
    units = "px",
    pointsize = 50)
data_price <- diamondsDF_new$price
data_carat <- diamondsDF_new$carat
data_cut <- diamondsDF_new$cut
levels(data_cut)
cut_fair <- subset(diamondsDF, cut == "Fair")
cut_good <- subset(diamondsDF, cut == "Good")
cut_very_good <- subset(diamondsDF, cut == "Very Good")
cut_premium <- subset(diamondsDF, cut == "Premium")
cut_ideal <- subset(diamondsDF, cut == "Ideal")

plot(cut_fair$carat, cut_fair$price,
     main = "Price vs. Carat by Cut", 
     xlab = "Carat", 
     ylab = "Price",
     col = "#119DA4", 
     pch = 22,
     cex = 1,
     xlim = range(diamondsDF$carat), 
     ylim = range(diamondsDF$price))

points(cut_good$carat, cut_good$price, col = "#FF6F61", pch = 23, cex = 0.6)
points(cut_very_good$carat, cut_very_good$price, col = "#6B5B95", pch = 24, cex = 0.6)
points(cut_premium$carat, cut_premium$price, col = "#88B04B", pch = 25, cex = 0.4)
points(cut_ideal$carat, cut_ideal$price, col = "#E9C46A", pch = 21, cex = 0.2)
#A few more harmonious colors
legend("topright", legend = c("Fair", "Good", "Very Good", "Premium", "Ideal"),
       col = c("#119DA4", "#FF6F61", "#6B5B95", "#88B04B", "#E9C46A"), 
       pch = c(22, 23, 24, 25, 21))
box()
dev.off()
```



## E09

Consider the variable carat in the diamondsDF dataframe. Transform this variable with the natural logarithm. Put in the same graphical window the following graphs: histogram with overlapped a kernel density estimate of the pdf
```{r}
data_carat <- diamondsDF_new$carat
log_data_carat <- log(data_carat)


plot(density(log_data_carat), col = "red", lwd = 2, xlab = "Values",xlim = c(-3,3))
hist(log_data_carat, probability = TRUE, col = rgb(1, 0, 0, 0.5),breaks=20,add=TRUE)
```

## E10

quantile-quantile plot with the reference line in red (Normal). 
```{r}
qqnorm(log_data_carat)
qqline(log_data_carat,
       col=2,lwd=3)
```

dotchart plot of the ecdf of carat (log-transformed) with overlapped the cumulative pdf of a Normal distribution.
```{r}
ecdf_log_data_carat <- ecdf(log_data_carat)
plot(ecdf_log_data_carat,
         xlab="log_data carat",
         ylab="cumulative density",
         ylim=c(0,1),
         xlim=c(-3,3),
         lwd = 2)
x <- seq(-3,3,length = 100)
y <- pnorm(x,0,1)
lines(x,y,col="red",type = "l",lwd = 2)

legend("bottomright", legend = c("ecdf of log carta", "cumulative pdf of norm"),
       col = c("black", "red"), 
       pch = c("l","l"))
```

