---
title: "assignment 3"
author: "wang yuhang"
date: "2024-10-14"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
    number_sections: true
    df_print: paged
  word_document:
    toc: true
    number_sections: true
editor_options: 
  chunk_output_type: inline
---
# Assignment 03

The diamonds case study
This case study is dataframe with rows and variables (sample space within brackets):

  - price: price in US dollars ($326–$18,823)
  
  - arat: weight of the diamond (0.2–5.01)
  
  - cut: quality of the cut (Fair, Good, Very Good, Premium, Ideal)
  
  - color: diamond colour, from D (best) to J (worst)
  
  - clarity: a measurement of how clear the diamond is (I1 (worst), SI2, SI1, VS2, VS1, VVS2, VVS1, IF (best))
  
  - x: length in mm (0–10.74)
  
  - y: width in mm (0–58.9)
  
  - z: depth in mm (0–31.8)
  
  - depth: total depth percentage = z / mean(x, y) = 2 * z / (x + y) thus (43–79)
  
  - table: width of top of diamond relative to widest point (43–95)
  
After downloading from myAriel the diamondsDF.RData file into the working directory, load this dataset into the workspace and obtain the subdataframe of complete cases: call this object wkDF.



## E00

Consider the variable price in the diamonds case study and create a working DataFrame called wkDF made by complete cases. Build a quantile-quantile plot with a red reference line.

```{r}

getwd()
dir()

load(file = "data/diamondsDF.RData")

wkDF <- diamondsDF

dim(wkDF)

names(wkDF)

head(wkDF)

tail(wkDF)

str(wkDF)
```
```{r}
qqnorm(wkDF$price)
qqline(wkDF$price,col=2,lwd=3)
```

## E01

Do the same as point (1) after taking the natural logarithm of price.

```{r}

log_price <- log(wkDF$price)

qqnorm(log_price)
qqline(log_price,col=2,lwd=3)
```

## E02

Calculate the ecdf of the variable in (1) after standardization of price (new variable priceS) and put the reference Normal cdf (parameters and ) as red line in the same plot. 

```{r}

priceS <- scale(log_price)
ecdf_s_price <- ecdf(priceS)
plot(ecdf_s_price,
         xlab="standardization of price",
         ylab="cumulative density",
         lwd = 2)

x <- seq(-4,4,length=1000)
y <- pnorm(x,0,1)
lines(x,y,col="red",type = "l",lwd = 2)
#Is the family of normal pdfs suited to our case study from the above plots?
#yes, because the line of the ecdf of the variable priceS is very similar with standard normal distribution.
```

## E03

Now split the complete cases of diamondsDF dataframe according to the R factors cut and color; allow the deletion of empty groups. Call the resulting R object wk_split. How many groups are expected and how many appear in the result?

```{r}


print("How many groups are expected?")
length(levels(wkDF$cut))*length(levels(wkDF$color))

# using complete.cases() to search without empty row
complete_diamonds_wkDF <- wkDF[complete.cases(wkDF), ]

# accordance with cut and color to split data set
wk_split <- split(complete_diamonds_wkDF, list(complete_diamonds_wkDF$cut, complete_diamonds_wkDF$color), drop = TRUE)

#showing the result
print("How many appear in the result?")
print(length(wk_split))



```
```{r}
#Print the vector of strings describing the cartesian product of the two sets of labels (for cut and color) using outer.
X <- (levels(complete_diamonds_wkDF$cut))
Y <- (levels(complete_diamonds_wkDF$color))
output_of_group_name <- outer(X, Y, FUN = paste)
output_of_group_name

```

## E04

Put the qqplot-qqline output of the first 9 groups into the same graphical window using wk_split for the standardized variable priceS within each group.

```{r}
 
wk_split_1_9 <- wk_split[1:9]
for (i in 1:9) {
    #assign function can assign the value to the key name,just use <- or = maybe bring error
    assign(paste("wk_split_1_9_s_",i,sep=""),scale(wk_split_1_9[[i]]$price))
    
}
#mfrow means setting the window's scale as n*m grids.
par(mfrow = c(3, 3))
qqnorm(wk_split_1_9_s_1,main = "Normal QQ Plot 1",xlim=c(-4,4))
qqline(wk_split_1_9_s_1,col="red")
qqnorm(wk_split_1_9_s_2,main = "Normal QQ Plot 2",xlim=c(-4,4))
qqline(wk_split_1_9_s_2,col="red")
qqnorm(wk_split_1_9_s_3,main = "Normal QQ Plot 3",xlim=c(-4,4))
qqline(wk_split_1_9_s_3,col="red")
qqnorm(wk_split_1_9_s_4,main = "Normal QQ Plot 4",xlim=c(-4,4))
qqline(wk_split_1_9_s_4,col="red")
qqnorm(wk_split_1_9_s_5,main = "Normal QQ Plot 5",xlim=c(-4,4))
qqline(wk_split_1_9_s_5,col="red")
qqnorm(wk_split_1_9_s_6,main = "Normal QQ Plot 6",xlim=c(-4,4))
qqline(wk_split_1_9_s_6,col="red")
qqnorm(wk_split_1_9_s_7,main = "Normal QQ Plot 7",xlim=c(-4,4))
qqline(wk_split_1_9_s_7,col="red")
qqnorm(wk_split_1_9_s_8,main = "Normal QQ Plot 8",xlim=c(-4,4))
qqline(wk_split_1_9_s_8,col="red")
qqnorm(wk_split_1_9_s_9,main = "Normal QQ Plot 9",xlim=c(-4,4))
qqline(wk_split_1_9_s_9,col="red")
```


## E05

Repeat point (5) for variable priceS (standardized within groups) but with histograms of relative frequency instead of qqplots. Use the same range for all the nine plots on the horizontal axis. The main title on top of each histogram is the group index 1,2,...
```{r}

library(ggplot2)
library(patchwork)

p1 <- ggplot(data.frame(value = wk_split_1_9_s_1), aes(x = value, y = after_stat(density))) +
      geom_histogram(binwidth = 0.2, fill = "orange", color = "black") +
      ggtitle("the group index 1") +
      theme_bw()+
      xlim(-2,4)+
      ylim(0,0.8)+
      theme(
        plot.title = element_text(hjust = 0.5))#theme could set the area of the title

p2 <- ggplot(data.frame(value =wk_split_1_9_s_2), aes(x = value, y = after_stat(density))) +
      geom_histogram(binwidth = 0.2, fill = "blue", color = "black") +
      ggtitle("the group index 2") +
      theme_bw()+
      xlim(-2,4)+
      ylim(0,0.8)+
      theme(
        plot.title = element_text(hjust = 0.5))#theme could set the area of the title

p3 <- ggplot(data.frame(value=wk_split_1_9_s_3), aes(x = value, y = after_stat(density))) +
      geom_histogram(binwidth = 0.2, fill = "green", color = "black") +
      ggtitle("the group index 3") +
      theme_bw()+
      xlim(-2,4)+
      ylim(0,0.8)+
      theme(
        plot.title = element_text(hjust = 0.5))#theme could set the area of the title
p4 <- ggplot(data.frame(value=wk_split_1_9_s_4), aes(x = value, y = after_stat(density))) +
      geom_histogram(binwidth = 0.2, fill = "orange", color = "black") +
      ggtitle("the group index 4") +
      theme_bw()+
      xlim(-2,4)+
  ylim(0,0.8)+
      theme(
        plot.title = element_text(hjust = 0.5))#theme could set the area of the title
p5 <- ggplot(data.frame(value=wk_split_1_9_s_5), aes(x = value, y = after_stat(density))) +
      geom_histogram(binwidth = 0.2, fill = "blue", color = "black") +
      ggtitle("the group index 5") +
      theme_bw()+
      xlim(-2,4)+
  ylim(0,1)+
      theme(
        plot.title = element_text(hjust = 0.5))#theme could set the area of the title

p6 <- ggplot(data.frame(value=wk_split_1_9_s_6), aes(x = value, y = after_stat(density))) +
      geom_histogram(binwidth = 0.2, fill = "green", color = "black") +
      ggtitle("the group index 6") +
      theme_bw()+
      xlim(-2,4)+
  ylim(0,0.8)+
      theme(
        plot.title = element_text(hjust = 0.5))#theme could set the area of the title

p7 <- ggplot(data.frame(value=wk_split_1_9_s_7), aes(x = value, y = after_stat(density))) +
      geom_histogram(binwidth = 0.2, fill = "orange", color = "black") +
      ggtitle("the group index 7") +
      theme_bw()+
      xlim(-2,4)+
  ylim(0,0.8)+
      theme(
        plot.title = element_text(hjust = 0.5))#theme could set the area of the title
p8 <- ggplot(data.frame(value=wk_split_1_9_s_8), aes(x = value, y = after_stat(density))) +
      geom_histogram(binwidth = 0.2, fill = "blue", color = "black") +
      ggtitle("the group index 8") +
      theme_bw()+
      xlim(-2,4)+
  ylim(0,0.8)+
      theme(
        plot.title = element_text(hjust = 0.5))#theme could set the area of the title

p9 <- ggplot(data.frame(value=wk_split_1_9_s_9), aes(x = value, y = after_stat(density))) +
      geom_histogram(binwidth = 0.2, fill = "green", color = "black") +
      ggtitle("the group index 9") +
      theme_bw()+
      xlim(-2,4)+
  ylim(0,1.25)+
      theme(
        plot.title = element_text(hjust = 0.5))#theme could set the area of the title


((p1 | p2 | p3) / (p4 | p5 | p6) / (p7 | p8 | p9)) 
#there are some warnings because we use the same of the range of x axis, 
#so some stray data(I just say it or range-out data) will lost.
```

## E06

Calculate mean and standard deviation of price for each group defined above using the two factors cut and color. Then, calculate the endpoints of intervals defined by mean standard deviation. Calculate the minimum of left endpoints and the maximum of right endpoints: call it xlim_scale.

```{r}
#Calculate all 35 groups' mean and standard deviation.
wk_split_1_35 <- wk_split[1:35]
for (i in 1:35) {
    #assign function can assign the value to the key name,just use <- or = maybe bring error
    assign(paste("wk_split_1_35_s_",i,sep=""),scale(wk_split_1_35[[i]]$price))
    
}
#I want to save the sd and mean as a dataframe maybe it is convenient for next steps.
sd_meanData <- data.frame(groupName=character(), sdValue=numeric(), meanValue=numeric())
for (i in 1:35) {
    sd_for_wk_split = assign(paste("wk_split_1_35_sd_",i,sep=""),sd(wk_split_1_35[[i]]$price))
    mean_for_wk_split = assign(paste("wk_split_1_35_mean_",i,sep=""),mean(wk_split_1_35[[i]]$price))
    #I create a new line and add it to the old dataframe as rbind
    new_row <- data.frame(groupName=output_of_group_name[i], sdValue=sd_for_wk_split, meanValue=mean_for_wk_split)
    sd_meanData <- rbind(sd_meanData, new_row)
    cat(i," group's ","sd: ", sd_for_wk_split,"mean: ",mean_for_wk_split,"\n")
    
}


```
```{r}
#we want to calculate the endpoints, I consider the left endpoint is mean-sd and the right endpoint is mean+sd.

sd_meanData$left_endpoint <- sd_meanData$meanValue - sd_meanData$sdValue
sd_meanData$right_endpoint <- sd_meanData$meanValue + sd_meanData$sdValue
sd_meanData$xlim_scale <- paste("(",sd_meanData$left_endpoint,sd_meanData$right_endpoint,")")
sd_meanData
sd_meanData$xlim_scale
```

## E07

Plot an horizontal segment with endpoints defined by mean standard deviation of price for each subgroup cut-color defined above, without scaling the raw data. Add a point on each segment to represent the mean value, red color, square symbol

```{r}

ggplot(sd_meanData, aes(x = left_endpoint, y = 1, xend = right_endpoint, yend = 1)) +
  geom_segment(color = "green", size = 1) +  
  labs(title = "Horizontal Segments", x = "X Axis", y = "Y Axis")+
  theme_bw()+
  geom_point(aes((left_endpoint+right_endpoint)/2), 
             colour = "red", 
             fill = "red", 
             shape=22, 
             size=3)+
  facet_wrap(facets = vars(groupName),
             ncol = 5,
             nrow = 7)
```

## E08

Add to the plot in figure 8 a vertical line passing through the marginal mean of price, color blue, double thickness. Put small black points at the end of each segment.

```{r}
#the marginal mean of price is different with the mean, the former one always has some conditional restriction, such as we devide 35 subgroups every group all has their own marginal mean.
ggplot(sd_meanData, aes(x = left_endpoint, y = 1, xend = right_endpoint, yend = 1)) +
  geom_segment(color = "green", size = 1) +  
  labs(title = "Horizontal Segments", x = "X Axis", y = "Y Axis")+
  theme_bw()+
  geom_point(aes((left_endpoint+right_endpoint)/2), 
             colour = "red", 
             fill = "red", 
             shape=22, 
             size=3)+
  geom_point(aes(right_endpoint), 
             colour = "black", 
             fill = "black", 
             shape=21, 
             size=1.5)+
  geom_vline(aes(xintercept=(left_endpoint+right_endpoint)/2),
             color = "blue",
             size = 1)+
  facet_wrap(facets = vars(groupName),
             ncol = 5,
             nrow = 7)

```


